Reading Notes

### 2020-07-30 2pd.tex
added notes from swc papers

\section*{Research Objectives}
<gain insight into the limits of coarse graining>
<create models for new opv compounds>
<create a workflow that will make creating new models more accessible>
<develop new tools that help humans do science>
<I don't know where to put this but I want a section on best practices>
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}

>>>>

\section*{Research Objectives}
<gain insight into the limits of coarse graining>
<create models for new opv compounds>
<create a workflow that will make creating new models more accessible>
<develop new tools that help humans do science>
<use that science to help solve energy crisis???????>
<I don't know where to put this but I want a section on best practices>
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
live coding, interactive \cite{Wilson2016}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}
